\pkg{casebase}: An Alternative Framework For Survival Analysis

### 2020-01-16 analysis/paper/paper.Rmd
mostly Done
I fixed a few of Max's comments, but some I was not certain about. particularly what to do with CFC's own package methods exploration. they dove into aspects I did not attempt to cover in the casebase lit review. NOTE: cmprsk was found in initial scraper, but was ignored in the manual pass through.

The final plot no longer uses a single individual but averages all individuals in our dataset. still uses our work around. Next I will attempt to use riskRegression and compare.

need to add timereg (riskregression is a wrapper for timereg)

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  echo = TRUE,
  comment = "#>",
  fig.path = "../figures/"
)
options(kableExtra.latex.load_packages = FALSE)
library(tidyverse)
library(magrittr)
library(survival)
#library(casebase)
devtools::load_all('../../../casebase')#testing
library(splines)
library(tibble)
library(glmnet)
library(kableExtra)
options(digits = 2, scipen = 999)
# set the seed for reproducible output
set.seed(1234)

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  echo = TRUE,
  comment = "#>",
  fig.path = "../figures/"
)
options(kableExtra.latex.load_packages = FALSE)
library(tidyverse)
library(magrittr)
library(survival)
library(casebase)
#devtools::load_all('../../../casebase')#testing
library(splines)
library(tibble)
library(glmnet)
library(kableExtra)
options(digits = 2, scipen = 999)
# set the seed for reproducible output
set.seed(1234)
